---
title: "Tutorial of LinearRegression and StepSelect"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial of LinearRegression and StepSelect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
install.packages("bench", repos="http://cran.us.r-project.org")
install.packages("MASS", repos="http://cran.us.r-project.org")
library(LinReg.Select)
```

### LinearReg

When fitting a linear regression model, it will also automatically generate a summary for the result of the linear regression:
```{r}
my.lm = LinearReg(mpg ~ cyl + disp + hp, data = mtcars)
```

Some features, like residuals, fitted values, R square, adjusted R square, etc., can also be retrieved from the function:
```{r}
plot(my.lm$fitted.values, my.lm$residuals)
my.lm$`Multiple R-squared`
my.lm$`Adjusted R-squared`
```

The function can also take interaction terms or terms with power:
```{r}
my.lm2 = LinearReg(mpg ~ cyl + disp + hp + cyl*disp + I(hp^2), data = mtcars)
```

To fit linear regression model without intercept:
```{r}
my.lm3 = LinearReg(mpg ~ -1 + cyl + disp + hp + cyl*disp, data = mtcars)
```


```{r}
ref = lm(mpg ~ cyl + disp + hp, data = mtcars)
my.result = LinearReg(mpg ~ cyl + disp + hp, data = mtcars)

all.equal(ref$coefficients, my.result$coefficients)
all.equal(ref$fitted.values, my.result$fitted.values)
all.equal(ref$residuals, my.result$residuals)
```

```{r}
result1 = bench::mark(LinearReg(mpg ~ cyl + disp + hp, data = mtcars)$`Multiple R-squared`, summary(lm(mpg ~ cyl + disp + hp, data = mtcars))$r.squared)
print(result1)

result2 = bench::mark(LinearReg(mpg ~ cyl + disp + hp, data = mtcars)$`Adjusted R-squared`, summary(lm(mpg ~ cyl + disp + hp, data = mtcars))$adj.r.squared)
print(result2)
```

### StepSelect

#### Backward Selection

To conduct backward selection:
```{r}
full_lm = lm(mpg ~ ., data = mtcars)
StepSelect(full_lm, direction = "backward")
```

k is the penalty used in AIC, the default is 2 but it can be defined by users:
```{r}
n = dim(mtcars)[1]
StepSelect(full_lm, direction = "backward", k = log(n))
```

Users can also trace the whole process by turning on the trace option:
```{r}
StepSelect(full_lm, direction = "backward", k = log(n), trace = TRUE)
```

To check the result of my backward selection function with the reference function stepAIC:
```{r}
ref = MASS::stepAIC(full_lm, direction = "backward", k = log(n), trace = FALSE)
my = StepSelect(full_lm, direction = "backward", k = log(n), trace = FALSE)
all.equal(ref$coefficients, my$coefficients)
all.equal(ref$call$formula, my$call$formula)
```

To compare the efficiency of my backward selection function with stepAIC function:
```{r}
result = bench::mark(MASS::stepAIC(full_lm, direction = "backward", k = log(n), trace = FALSE)$coefficients, StepSelect(full_lm, direction = "backward", k = log(n), trace = FALSE)$coefficients, )
print(result)
```

#### Forward Selection

To conduct forward selection:
```{r}
StepSelect(full_lm, direction = "forward")
```

Similarly, users can also define k and trace:
```{r}
StepSelect(full_lm, direction = "forward", k = log(n), trace = TRUE)
```

To check the result of my backward selection function with the reference function stepAIC:
```{r}
m = lm(mpg ~ 1, data = mtcars)
ref2 = MASS::stepAIC(m, direction="forward", k = log(n), scope=list(lower=m, upper=full_lm), trace = FALSE)
my2 = StepSelect(full_lm, direction = "forward", k = log(n), trace = FALSE)
all.equal(ref2$coefficients, my2$coefficients)
all.equal(ref2$call$formula, my2$call$formula)
```


To compare the efficiency of my forward selection function with stepAIC function:
```{r}
result = bench::mark(MASS::stepAIC(m, direction="forward", k = log(n), scope=list(lower=m, upper=full_lm), trace = FALSE)$coefficients, my2 = StepSelect(full_lm, direction = "forward", k = log(n), trace = FALSE)$coefficients)
print(result)
```

